Title

### 2018-08-08 thesis/paper/paper.tex
Fixed variabels in require pattern to allow for conjunction-reuse
FIX: Multi-Value rules

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(O, t) \leftarrow \text{next}(S, O) \wedge \text{require}(S, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the rules are
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(O, X, C, t) \leftarrow \text{next}(S, P, V, O, X, C) \wedge \text{require}(S, P, V, t) \wedge c
\end{equation*}

@@

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is \(c = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)\). The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(Q, R) \wedge \text{next}(R, S) \wedge \text{require}(Q) \wedge t
\end{equation*}
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \text{require\_second}(R) \wedge t
\end{equation*}
A violations would be any last statement requiring a second constrained statement.

>>>>

For statements the pattern consists of two rules, both utilising the same conjunction \(c = C_1 \wedge .. \wedge C_m\) with arbitrary atoms \(C_n\) which is used to test if the statement does not fulfil the requirement. Then rule one
\begin{equation*}
\text{require}(S, t) \leftarrow \text{first}(S, I) \wedge c
\end{equation*}
states that the statement requires the condition and
\begin{equation*}
\text{require}(S, t) \leftarrow \text{next}(O, S) \wedge \text{require}(O, t) \wedge c
\end{equation*}
propagates this down the statement chain.

For qualifiers the rules are
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{first}(S, P, V) \wedge c
\end{equation*}
\begin{equation*}
\text{require}(S, P, V, t) \leftarrow \text{next}(O, X, C, S, P, V) \wedge \text{require}(O, X, C, t) \wedge c
\end{equation*}

@@

\subsection{Multi-value (Q21510857)}
The multi-value constraint requires a limited count of constrained statements. Alternatively, it could be said that if the item requires a second statement, the constraint is violated. Pre-processing extracts all items statements and inequality between all item statement properties as usual and the conjunction is \(c = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{propertyConstant}, P)\). The predicate require\_second\([2]\) is introduced with the same meaning as require except that it will be applied after a required property has been found:
\begin{equation*}
\begin{split}
\text{require\_second}&(S, \text{propertyConstant}) \leftarrow \\
&\text{next}(Q, R) \wedge \text{next}(R, S) \wedge \text{require}(Q, \text{propertyConstant}) \wedge t \wedge \\
&\text{tripleEDB}(R, I, \text{propertyConstant}, C)
\end{split}
\end{equation*}
\begin{equation*}
\text{require\_second}(S, \text{propertyConstant}) \leftarrow \text{next}(R, S) \wedge \text{require\_second}(R, \text{propertyConstant}) \wedge t
\end{equation*}
A violations would be any last statement requiring a second constrained statement.\\
